---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to the soundscapeR Tutorial 

## 1. Installing the tutorial
\
**To install this tutorial for the [soundscapeR]() R-package, please run:** \
\
```{r, eval=FALSE }

devtools::install_github(repo = "ThomasLuypaert/soundscapeR.tutorial")

```
\

## 2. Running the tutorial
\
**Once the package installed, load the package using:** \
\
```{r, eval=FALSE}

library(soundscapeR.tutorial)

```
\
**Finally, to run the tutorial, use:** \
\
```{r, eval=FALSE}

shiny_args <- list(launch.browser = getOption("shiny.launch.browser", interactive()))

learnr::run_tutorial(name = "soundscapeR_tutorial", package = "soundscapeR.tutorial", shiny_args = shiny_args)

```

## 3. The accompanying slides
\
If you're interested in the slide deck that accompanies this tutorial, you can find the slides on Part I: Collecting acoustic data using AudioMoth [here](https://docs.google.com/presentation/d/1NtVe3vXpoF1uVDwj0k0U8TbBa1LmwTGKGmA4fEmlW6I/edit?usp=sharing), and the slides on Part II: A soundscape approach to analysing big acoustic data [here](https://docs.google.com/presentation/d/1yU6hUVBs7OeNlraAe8xGulqO2Yp4gFCd88asXrzaZFM/edit?usp=sharing). 
